### 2025-07-23 getting-started.qmd
20250723 - additions

@@

- numeric indices of the rows/columns to keep (or drop)
- names of the rows/columns to keep (or drop)
- values of `TRUE` and `FALSE` corresponding to which rows/columns to keep

@@

@@

@@

```{r}
dataLong <- dplyr::full_join(
  players %>% dplyr::select(-age),
  fantasyPoints_weekly,
  by = c("ID")
)

@@

>>>>

To subset a vector, use brackets to specify the elements to keep:

vector[elementsToKeep]
```

@@

- numeric indices of the elements/rows/columns to keep (or drop)
- names of the rows/columns to keep (or drop)
- values of `TRUE` and `FALSE` corresponding to which elements/rows/columns to keep

@@

Missing elements are stored in R as `NA`.
You can determine how many missing elements there are in a data frame using the following syntax:

```{r}
length(which(is.na(nfl_players)))
```

You can determine how many missing elements there are in a variable using the following syntax:

@@

You can determine how many non-missing elements there are in a data frame using the following syntax:

```{r}
length(which(!is.na(nfl_players)))
```

You can determine how many rows in the data frame have no missing data using the following syntax:

```{r}
nrow(na.omit(nfl_players))
```

You can determine how many non-missing elements there are in a vector using the following syntax:

@@

```{r}
dataLong <- dplyr::full_join(
  players %>% dplyr::select(-age),
  fantasyPoints_weekly,
  by = c("ID")
) %>% 
  arrange(ID, season, week)

@@

## Commenting Code {#sec-comment}

To comment your code, using the `#` sign.
Anything on the line that appears after the `#` sign will be interpreted as a comment and will not be evaluated by R.
It is important to comment your code frequently with what you are doing doing and why so that you and others know how to read it.

```{r}
x <- 1 # this line will run
       # this line will NOT run: x <- 2

x
```
